Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-07-09 manuscript/climate_sensitivity_SI.Rmd
replaced dAICc with ∆AICc in tables and table legends (now footnotes)

\newpage
```{r, Table S3, eval=TRUE, echo=FALSE, message=FALSE}
tableS3 <- read.csv("tables_figures/publication/tables3_drought_stats.csv", stringsAsFactors = FALSE)
kable(tableS3, booktabs=TRUE, format = "latex", caption = "Table S3: Palmer drought severity index (PDSI) by month for focal droughts. Rank refers to ") %>%
  pack_rows("focal droughts", 1, 4, latex_gap_space = ".4em", colnum = 3, hline_before = FALSE) %>%
  pack_rows("", 5, 8, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 9, 12, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("other", 13, 16, latex_gap_space = ".4em", colnum = 3, hline_before = FALSE) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```

\newpage
```{r table S4, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/tableS4_singlevariable_models_reform_arimaratio.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(singlevar_table, booktabs = TRUE, caption = "Table S4. Individual tests of species traits as drivers of drought resistance, where $Rt_{ARIMA}$ is used as the response variable. Delta AICc is the AICc of a model excluding the trait minus that of the model including it. Variable abbreviations are as in Table 2.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  pack_rows("Species traits", 1, 6, latex_gap_space = "1em", colnum = 3, hline_before = FALSE) %>%
  #mutate(dAICc = cell_spec(dAICc, "html", bold = ifelse(dAICc > 1.999, TRUE, FALSE))) %>%  #trying to put sig values in bold, but this doen't work
  kable_styling()
```
**$\Delta$AICc > 2: variable considered significant as an individual predictor

\newpage
```{r table S5, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS5_multivariable_models_reform_arimaratio.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S5. Summary of top full models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable. Models are ranked by AICc, and we show all models whose AICc value falls within 1.0 (Delta AICc<1) of the best model (bold).", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," "," "," ", " ", " ", "crown position" = 4, 
                     " "," ")) %>%
  pack_rows("", 1, 1, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 2, 2, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 3, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(2, bold = T) %>%
  row_spec(3, bold = T) %>%
  row_spec(5, bold = T) %>%
  kable_styling()
```

>>>>

\newpage
```{r, Table S3, eval=TRUE, echo=FALSE, message=FALSE}
tableS3 <- read.csv("tables_figures/publication/tables3_drought_stats.csv", stringsAsFactors = FALSE)
kable(tableS3, booktabs=TRUE, format = "latex", caption = "Table S3: Palmer drought severity index (PDSI) by month for focal droughts. ") %>%
  pack_rows("focal droughts", 1, 4, latex_gap_space = ".4em", colnum = 3, hline_before = FALSE) %>%
  pack_rows("", 5, 8, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 9, 12, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("other", 13, 16, latex_gap_space = ".4em", colnum = 3, hline_before = FALSE) %>%
  kable_styling(bootstrap_options = "striped", full_width = FALSE, latex_options = "hold_position")
```
Rank refers to ...**XX**

\newpage
```{r table S4, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/tableS4_singlevariable_models_reform_arimaratio.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(singlevar_table, booktabs = TRUE, caption = "Table S4. Individual tests of species traits as drivers of drought resistance, where $Rt_{ARIMA}$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  pack_rows("Species traits", 1, 6, latex_gap_space = "1em", colnum = 3, hline_before = FALSE) %>%
  #mutate(dAICc = cell_spec(dAICc, "html", bold = ifelse(dAICc > 1.999, TRUE, FALSE))) %>%  #trying to put sig values in bold, but this doen't work
  kable_styling()
```
Variable abbreviations are as in Table 2. 
$\Delta$AICc is the AICc of a model excluding the trait minus that of the model including it.

**$\Delta$AICc > 2: variable considered significant as an individual predictor

\newpage
```{r table S5, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/tableS5_multivariable_models_reform_arimaratio.csv", stringsAsFactors = FALSE, check.names = FALSE) 
kable(multivar_table, booktabs = TRUE, caption = "Table S5. Summary of top full models for each drought instance, where $Rt_{ARIMA}$ is used as the response variable. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," "," "," ", " ", " ", "crown position" = 4, 
                     " "," ")) %>%
  pack_rows("", 1, 1, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 2, 2, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 3, 4, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 5, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(2, bold = T) %>%
  row_spec(3, bold = T) %>%
  row_spec(5, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 1.0 ($\Delta$AICc<1) of the best model (bold).

### 2020-07-09 manuscript/tables&figures.Rmd
replaced dAICc with ∆AICc in tables and table legends (now footnotes)

\clearpage
```{r table 4, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/table4_singlevariable_models_reform.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_all.csv`.
kable(singlevar_table, booktabs = TRUE, caption = "Table 4. Individual tests of species traits as drivers of drought resistance ($Rt$ metric). Delta AICc is the AICc of a model excluding the trait minus that of the model including it. Variable abbreviations are as in Table 2.", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  pack_rows("Species traits", 1, 6, latex_gap_space = "1em", colnum = 3, hline_before = FALSE) %>%
  #mutate(dAICc = cell_spec(dAICc, "html", bold = ifelse(dAICc > 1.999, TRUE, FALSE))) %>%  #trying to put sig values in bold, but this doesn't work
  kable_styling()
```
*$\Delta$AICc > 1: variable meets $\Delta$AICc criterion for inclusion in full model

@@

\clearpage
```{r table 5, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/table5_multivariable_models_reform.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_best_coeff.csv`.
kable(multivar_table, booktabs = TRUE, caption = "Table 5. Summary of top full models for each drought instance. Models are ranked by AICc, and we show all models whose AICc value falls within 1.0 (Delta AICc<1) of the best model (bold).", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," "," "," ", " ", " ", "crown position" = 4, 
                     " "," ")) %>%
  pack_rows("", 1, 1, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 2, 2, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 3, 3, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 4, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(2, bold = T) %>%
  row_spec(3, bold = T) %>%
  row_spec(4, bold = T) %>%
  kable_styling()
```

<!-- \clearpage -->
<!-- ```{r table 5, eval = TRUE, echo=FALSE, warning=FALSE} -->
<!-- # *****this is for if doing arimaratio!!!!***** -->
<!-- library(knitr) -->
<!-- library(kableExtra) -->
<!-- multivar_table <- read.csv("tables_figures/publication/table5_multivariable_models_arimaratio.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_best_coeff.csv`. -->
<!-- kable(multivar_table, booktabs = TRUE, caption = "Table 5. Summary of top full models for each drought instance. Models are ranked by AICc, and we show all models whose AICc value falls within 1.0 (dAICc<1) of the best model (bold).", format = 'latex', escape = FALSE) %>% -->
<!--   kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>% -->
<!--   add_header_above(c(" "," "," "," "," ", " ", " ", "xylem porosity" = 2," ", " ")) %>% -->
<!--   pack_rows("", 1, 2, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>% -->
<!--   pack_rows("", 3, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>% -->
<!--   pack_rows("", 6, 7, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>% -->
<!--   pack_rows("", 8, 11, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>% -->
<!--   row_spec(1, bold = T) %>% -->
<!--   row_spec(3, bold = T) %>% -->
<!--   row_spec(6, bold = T) %>% -->
<!--   row_spec(8, bold = T) %>% -->
<!--   kable_styling() -->
<!-- ``` -->

>>>>

\clearpage
```{r table 4, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
singlevar_table <- read.csv("tables_figures/publication/table4_singlevariable_models_reform.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_all.csv`.
kable(singlevar_table, booktabs = TRUE, caption = "Table 4. Individual tests of species traits as drivers of drought resistance ($Rt$ metric).", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," ","all droughts"=2,"1966"=2, "1977" = 2, "1999" = 2)) %>%
  pack_rows("Species traits", 1, 6, latex_gap_space = "1em", colnum = 3, hline_before = FALSE) %>%
  #mutate(dAICc = cell_spec(dAICc, "html", bold = ifelse(dAICc > 1.999, TRUE, FALSE))) %>%  #trying to put sig values in bold, but this doesn't work
  kable_styling()
```
Variable abbreviations are as in Table 2. 
$\Delta$AICc is the AICc of a model excluding the trait minus that of the model including it.

*$\Delta$AICc > 1: variable meets $\Delta$AICc criterion for inclusion in full model

@@

\clearpage
```{r table 5, eval = TRUE, echo=FALSE, warning=FALSE}
library(knitr)
library(kableExtra)
multivar_table <- read.csv("tables_figures/publication/table5_multivariable_models_reform.csv", stringsAsFactors = FALSE, check.names = FALSE) #note: this table is a rearranged version of `tested_traits_best_coeff.csv`.
kable(multivar_table, booktabs = TRUE, caption = "Table 5. Summary of top full models for each drought instance. ", format = 'latex', escape = FALSE) %>%
  kable_styling(latex_options = c("scale_down", "hold_position"), font_size = 12, protect_latex = TRUE) %>%
  add_header_above(c(" "," "," "," "," ", " ", " ", "crown position" = 4, 
                     " "," ")) %>%
  pack_rows("", 1, 1, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 2, 2, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 3, 3, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  pack_rows("", 4, 5, latex_gap_space = ".4em", colnum = 1, hline_before = FALSE) %>%
  row_spec(1, bold = T) %>%
  row_spec(2, bold = T) %>%
  row_spec(3, bold = T) %>%
  row_spec(4, bold = T) %>%
  kable_styling()
```
Models are ranked by AICc. Shown are all models whose AICc value falls within 1.0 ($\Delta$AICc<1) of the best model (bold).
